### 2021-05-05 README.Rmd
Flush out old files and start anew

<!-- badges: start -->
[![R-CMD-check](https://github.com/jolars/LookAheadScreening/workflows/R-CMD-check/badge.svg)](https://github.com/jolars/HessianScreening/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/jolars/LookAheadScreening/workflows/R-CMD-check/badge.svg)](https://github.com/jolars/LookAheadScreening/actions)
<!-- badges: end -->
